---
title: "Luxembourg Research Evaluation 2022"
author: "Daniel S. Hain"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  pdf_document:
    toc: no
  html_notebook:
    df_print: paged
    toc: no
    code_folding: hide
---

```{r setup, include=FALSE}
### Generic preamble
rm(list=ls())
Sys.setenv(LANG = "en")
options(scipen = 5)
set.seed(1337)

### Load packages  
library(knitr) # For display of the markdown
library(kableExtra) # For table styling

library(tidyverse)
library(magrittr)
```

```{r global_options, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE, 
                      message = FALSE)
```

```{r, include=FALSE}
var_inst<- 'LIH'
var_dept <- 'TMOH'
```

```{r, include=FALSE}
data <- read_tsv('../data/publications_lIH.txt')
colnames(data) <-colnames(data) %>% str_to_lower() %>% str_replace_all(' ', '_') %>% str_remove_all('[^[:alnum:]_]')

var_dept_list <- c('Department of Cancer Research', 'Department of Infection and Immunity', 'Department of Precision Health', 'Translational Medicine Operations Hub', 'Transversal Translational Medicine')

data %<>% filter(year >= 2018, year <=2021) %>% 
  mutate(doi = dois_digital_object_identifiers %>% str_remove('^.*doi.org/') %>% str_remove('^.*dx\\.') %>% str_remove(' ') %>% str_replace_all('%', '/')) %>%
   filter(parent_organisational_units %in% var_dept_list) %>%
  mutate(unit_short = case_when(
    parent_organisational_units == 'Department of Cancer Research' ~ "DCR",
    parent_organisational_units == 'Department of Infection and Immunity' ~ "DII",
    parent_organisational_units == 'Department of Precision Health' ~ "DPH",
    parent_organisational_units == 'Translational Medicine Operations Hub' ~ "TMOH",
    parent_organisational_units == 'Transversal Translational Medicine' ~ "TMOH")
  ) %>%
  group_by(pure_id) %>%
    arrange(pure_id, doi) %>%
    fill(doi, .direction = 'downup') %>%
  ungroup() %>%
  distinct(pure_id, unit_short, .keep_all = TRUE) %>%
  # load matching errors from SciVal
  left_join(read_csv2('../output/pub_doi_unmatched.csv') %>% filter(institute == var_inst) %>% select(doi, issue), by = 'doi') %>%
  mutate(issue = if_else(is.na(doi), 'missing DOI', issue))

```


```{r, include=FALSE}
data %<>%
  filter(unit_short == var_dept) %>%
  drop_na(issue)
```

# Introduction

The bibliometric part of the 2022 research evaluation is based on Scopus data, one of the most comprehensive providers of academic publications. However, some potentially relevant scholarly output is not covered. Reasons might be that the publication outlet is not Scopus indexed. While most academic journals are, the coverage of bookchapters and conference proceedings is less exhaustive. In rare cases, errors in the database can also lead to underreporting.

To get an exhaustive overview covering all scholarly output, find below a breakdown of publications not matched with Scopus, and therefore not included in the overal evaluation.

# By Type

```{r}
data %>%
  count(issue, year) %>%
  ggplot(aes(x = year, y = n, fill = issue)) + 
  geom_col() +
  theme(legend.position = 'bottom') +
  labs(title = paste(var_inst, 'publications dept.', var_dept, 'not included in reporting', sep = ' '),
       subtitle = 'By reason',
       x = 'Year', y = 'Number of Publications')
```

```{r}
data %>%
  count(type, year) %>%
  ggplot(aes(x = year, y = n, fill = type)) + 
  geom_col() +
  theme(legend.position = 'bottom') +
  labs(title = paste(var_inst, 'publications dept.', var_dept, 'not included in reporting', sep = ' '),
       subtitle = 'By publication type',
       x = 'Year', y = 'Number of Publications')
```

# By outlet (Journal articles only)

```{r results='asis'}
data %>%
  filter(type == 'Article') %>%
  mutate(journal_title = journal_title %>% str_replace_all("[^[:alnum:]]", " ") ) %>%
  count(journal_title, sort = TRUE) %>%
  kable(booktabs = TRUE, caption = "Outlet of unmatched journal publication", position = '!ht') 
```


